### 2022-03-01 extension.rmd
Make the Makefile emit docx; trim to under 8900 words
For IJOC; the emitted docx still needs some manual work, e.g. chopping
the equations etc.. But this is the most reproducible workflow one can
get for a journal only processing docx.

author: 
  - name          : "Chung-hong Chan"
    affiliation   : "1"
    corresponding : yes
    address       : "A5, 6 (section A), 68159 Mannheim, Germany"
    email         : "chung-hong.chan@mzes.uni-mannheim.de"
  - name          : "Adrian Rauschfleisch"
    affiliation   : "2"

affiliation:
  - id            : "1"
    institution   : "Mannheimer Zentrum für Europäische Sozialforschung, Universität Mannheim, Germany"
  - id            : "2"
    institution   : "National Taiwan University, Taiwan"

@@

>>>>

# author: 
#   - name          : "Chung-hong Chan"
#     affiliation   : "1"
#     corresponding : yes
#     address       : "A5, 6 (section A), 68159 Mannheim, Germany"
#     email         : "chung-hong.chan@mzes.uni-mannheim.de"
#   - name          : "Adrian Rauschfleisch"
#     affiliation   : "2"

# affiliation:
#   - id            : "1"
#     institution   : "Mannheimer Zentrum für Europäische Sozialforschung, Universität Mannheim, Germany"
#   - id            : "2"
#     institution   : "National Taiwan University, Taiwan"

@@

# Source Code

All source will be available on the author(s)' Github upon acceptance. The following are key code chunks used in the paper.

## Expression of outlet-level models in lme4 and brms

```r
require(brms)
require(lme4)
# brms
brm(z ~ offset(log(n)) + (1|k)+log(x),
          family = negbinomial(), data = outlet_data)
# lme4
glmer.nb(z ~ offset(log(n)) + (1|k) + log(x), data = outlet_data)
```

## Expression of disaggregated out-level model in MASS

```r
require(MASS)
glm.nb(z ~ offset(log(n)) + log(x), data = outlet_data)
```

## Expression of article-level models in lme4 and brms

```r
brm(y~(1|k/j)+log(x), family = bernoulli(), data = article_data)
glmmer(y~(1|k/j)+log(x), family = binomial(), data = article_data)
```

## Expression of disaggregated article-level model in MASS

```r
glm(y ~ log(x), family = binomial(), data = article_data)
```

## Setting up weakly informative prior in the brms model

```r
weaklyinformative_prior <- c(prior_string("normal(0, 1)",
                                          class = "b"),
                             prior_string("normal(0, 1)",
                                          class = "Intercept"))
# The sample_prior argument is optional. But useful for further analysis.
import_brms <- brm(z~offset(log(n))+(1|k)+log(x_import),
          data = outlet_data, family = negbinomial(),
          prior = weaklyinformative_prior, sample_prior = TRUE)
import_brms
```

## WJS: Estimation of prior

```r
beta_d_1 <- 0.15
sig_level <- 0.001
beta_d_1 / abs(qnorm(sig_level / 2))
```

## WJS: Full code

The cubic relationship can be set using the `I()` function.

```r
require(tidyverse)

informative_prior <- c(prior_string("normal(0, 1)", class = "b"),
                       prior_string("normal(0, 1)", class = "Intercept"),
                       prior_string("normal(0.14, 0.045)",
                                    class = "b", coef = "EXPRNCE"),
                       prior_string("normal(0.07, 0.027)",
                                    class = "b", coef = "RANK"))

std <- function(x){
  (x - mean(x, na.rm = TRUE))/sd(x, na.rm = TRUE)
}
## eiu is Index of Democracy, gdppc is GDP per capita (log)
set.seed(12121)
wjs %>%
    select(ppa, EXPRNCE, RANK, GENDER, UNI_EDU, UNI_EDU, eiu, gdppc, COUNTRY) %>%
    mutate(gdppc = log(gdppc), COUNTRY = as.factor(COUNTRY)) %>%
    mutate_at(vars(ppa:gdppc), std) -> wjs_processed
brm(ppa ~ EXPRNCE + RANK + GENDER + UNI_EDU + eiu + gdppc + (1|COUNTRY),
    data = wjs_processed, cores = 4, iter = 3000, prior = informative_prior,
        sample_prior = TRUE) -> ppa_mod

set.seed(12121)
## iter needs to set larger to ensure convergence
brm(ppa ~ EXPRNCE + RANK + GENDER + UNI_EDU + I(eiu^3) + gdppc + (1|COUNTRY),
    data = wjs_processed, cores = 4, iter = 4000, prior = informative_prior,
    sample_prior = TRUE) -> ppa_qmod
```

### 2022-03-01 manuscript.rmd
Make auto deanony. version
Make the Makefile emit docx; trim to under 8900 words
For IJOC; the emitted docx still needs some manual work, e.g. chopping
the equations etc.. But this is the most reproducible workflow one can
get for a journal only processing docx.

authornote: |
  The authors would like to thank professor Kasper Welbers (Vrije Universiteit Amsterdam) for his advice on the development of the Dutch dictionary; Dr Junior Yuner Zhu (City University of Hong Kong) for sharing details about her study.
  Source code and data are available at (redacted). Prereg: https://osf.io/2h4w8/

@@

*"The comparative approach attempts to reach conclusions beyond single cases and explains differences and similarities between objects of analysis against the backdrop of their contextual conditions."* @esser:2017:CRM

@@

This study of ecological effects on individual behaviors has a long tradition in social sciences. A famous example was Émile Durkheim's investigation on the ecological factors associated with suicide [@durkheim1897suicide]. Durkheim found a higher suicide rate among citizens from Scandinavian countries than those from other European countries. Using today’s standard, Durkheim's analysis is descriptive and this descriptive approach for studying ecological effect is indeed still useful for hypothesis generation in comparative research. An example of hypothesis-generating comparative research is @chan2020combining, in which the sentiment profiles of terrorism coverage from Muslim- and Christian-majority countries were visualized. Hypothesis-generating comparative study, however, is rare. Most studies have a confirmatory outlook. As we see from the example hypotheses above, most of these studies propose hypotheses to test for ecological effects. In this context usually traditional (frequentist) hypothesis testing approaches were used: @esser:2013:C lumped multiple outlets from the same country together and then used univariate analysis of variance to test for the differences in the proportion of opinion-orienting articles across countries. In @wu:2000:SDI, multiple stepwise regression was used. These approaches violate the underlying assumptions of the statistical analyses. It highlights the fact that comparative research introduces a feature that researchers usually overlook: media contents are clustered in a multilevel structure. A news article is nested within its media outlet and its media outlet is in turn nested within its country [^author]. Such data structure brings two problems: non-atomicity and non-stochasticity.

[^author]: Theoretically, with large enough data it can be argued that a news article is nested within authors.

@@

This method is the so-called "disaggregation approach". From an epistemic standpoint, searching for ecological effect by studying the value of slope ($\beta_{1}$) leads to atomistic fallacy [@hox2017multilevel]. From a statistical standpoint, this approach violates the underlying independence assumption. Almost all frequentist statistical tests assume that the observations are independent of each other: $y_{i}$ given $x_{i}$ are independently identically distributed (i.i.d.). Articles from the same media outlet are hardly i.i.d.: they are subjected to being edited by the same editorial team, to being written by the same group of journalists exposed to the same journalistic culture and paid for by the same employer. Also, the way communication researchers collect their media content resembles cluster sampling rather than random sampling: one usually starts from a specific media outlet and then collects all relevant articles from it. The choice of media outlets or countries is almost always not randomly selected. [^1] This sampling approach makes the independence assumption even more fragile.

[^1]: If countries were randomly selected, we shall see more African countries in comparative works. It is because 1/4, or 54 out of 195, UN countries are in Africa.

Previous simulation studies have shown that ignoring this dependence can lead to false-positive associations [e.g. @clarke:2008:W;@chen:2012:IIL]. The problem is more severe when the dependent variable is a discrete binary variable [@clarke:2008:W], a common feature of content analysis. [^2]

[^2]: The non-atomicity argument has been in standard statistics textbooks for 40+ years and it might look repetitious. We believe it is still necessary, not least because multilevel modeling --unlike what @mcelreath2020statistical [p. 356] said-- is still not the default regression approach in communication research for hierarchical data and there are many justifications for using the disaggregation approach, e.g. an example in @zhu:2020:S [footnote 5]. Even a multilevel modeling textbook advocates these justifications [@bickel2007multilevel]. See also @nezlek:2008:IMM for a criticism of these justifications.

@@

*"PROBABILITY DOES NOT EXIST."* Bruno de Finetti

What is the probability for this paper being accepted by *Journalism Studies*? Under the frequentist framework (and if *Journalism Studies* were accepting papers stochastically), we can only find this out by repeatedly submitting this paper to *Journalism Studies*, say for 100 times, and then count the frequency of acceptance in these repeated submissions. It is indeed impractical as well as inhumane to the editorial team of *Journalism Studies*. Instead, we assert before submission that this paper has a probability of 24% for being accepted. That is the published acceptance rate from *Journalism Studies*’s website. After this paper is submitted and is not desk rejected, the probability might be around 24% to 30%. After a month of waiting and our confidence is shaken a little, the probability might decrease to 10% to 20%. After the paper is favorably reviewed by two reviewers and an R&R is invited, the probability might increase to 40% to 60%. If you see this paper under the "Latest articles" section of *Journalism Studies*'s website, then the probability is beyond doubt 100% (or 0% if we submit this paper again).

@@

Undoubtedly, setting prior is consequential to the analysis [@van:2006:PB]. But the influence from priors is greatly weakened, when the data is getting bigger. Other than expert elicitation, another non-controversial way to specify priors --- at least in our opinion --- is to use  a weakly informative prior [@lemoine:2019:M]. In this way, one specifies only the possible range of the posterior [^4]. Some so-called "default weakly informative priors", e.g. $\mathcal{t}(1, 0, 0.25)$, have been suggested for typical regression models [@gelman:2008]. The documentation of Stan also provides information on how to choose an appropriate prior (https://github.com/stan-dev/stan/wiki/Prior-Choice-Recommendations).

[^4]: One could also use a completely *noninformative* prior such as $\mathcal{U}(-\infty, \infty)$. It is, however, no longer advised.

@@

*"There is a general challenge to a prescription of more widespread use of Bayesian methods for multilevel modeling, and that is that such methods require statistical expertise beyond that of most applied social science researchers, as well as specialist software (or software with which such researchers are unfamiliar)."* @bryan:2015:MMC [p. 19]

Bayesian analysis is still a minority statistical method in social sciences. It is reasonable to say that Bayesian analysis is extremely rare in our field. Although some communication researchers adopted the method [e.g. @kovic:2017:B;@chan2020high], these studies are not comparative. As far as we know, the only available comparative research in journalism studies that Bayesian multilevel regression was used for studying ecological effect are @leeuw:2020:AAT and @heidenreich:2022:DE. We believe comparative communication research fits the use case of Bayesian multilevel regression analysis. Although there is another methodological introduction to Bayesian analysis aiming at communication researchers [@konijn:2015:PSP], the main purpose of the rest of this paper is to demonstrate how to actually do the analysis using the R package *brms* [@burkner2017advanced]. As the interface of *brms* is almost the same as *lme4* [@bates:2015:FLM, another R package for fitting multilevel models using MLE], *lme4* users might find *brms* extremely familiar. The above-quoted challenge about the prescription of more widespread use of Bayesian methods for multilevel modeling is no longer an issue.

@@

We used only the data from 2019 as the baseline. It is important to note that the Hong Kong protests, the 30th anniversary of the Tiananmen Square Protests and the 70th anniversary of the communist regime were in that year. Also, it was at the zenith of the US-China trade war.

@@

In lme4 and brms, the above equation is expressed as such:

```r
require(brms)
require(lme4)
# brms
brm(z ~ offset(log(n)) + (1|k)+log(x),
          family = negbinomial(), data = outlet_data)
# lme4
glmer.nb(z ~ offset(log(n)) + (1|k) + log(x), data = outlet_data)
```

@@

In MASS, it is expressed as such:

```r
require(MASS)
glm.nb(z ~ offset(log(n)) + log(x), data = outlet_data)
```

@@

Or in lme4/brms code:

```r
brm(y~(1|k/j)+log(x), family = bernoulli(), data = article_data)
glmmer(y~(1|k/j)+log(x), family = binomial(), data = article_data)
```

@@

In MASS, it is expressed as such:

```r
glm(y ~ log(x), family = binomial(), data = article_data)
```

@@

All, except the prior for regression coefficients, are default priors suggested by *brms*. The prior can be set with the following R code.

```r
weaklyinformative_prior <- c(prior_string("normal(0, 1)",
                                          class = "b"),
                             prior_string("normal(0, 1)",
                                          class = "Intercept"))
# The sample_prior argument is optional. But useful for further analysis.
import_brms <- brm(z~offset(log(n))+(1|k)+log(x_import),
          data = outlet_data, family = negbinomial(),
          prior = weaklyinformative_prior, sample_prior = TRUE)
import_brms
```

@@

[^5]: HDI is one representation of the Bayesian credible interval. There should be no "correct" choice of the level of credibility but some established conventions. We choose, like many published works [e.g. @stegmueller:2013:HMC; @kovic:2017:B; @chan2020high], the default value of 95\%. However, there is a general concern about this credibility level as being unstable for Bayesian analysis [@kruschke2014doing]. Some Bayesians, notably Andrew Gelman, report very liberal 50\% credible intervals. @mcelreath2020statistical selects 89\% to show the arbitrariness of the practice. @leeuw:2020:AAT select 90\%.

@@

There are several diagnostic checks that we can do to make sure our model is valid.

* Increasing number of iterations

The first test is to increase the number of iterations from 2000 to a higher value, e.g. 4000, and see if the result is consistent with the initial analysis. This check makes sure our result is not transient due to short iteration time.

Increasing the number of iterations did change a bit of the estimates, but only at the second decimal place. It shows that the results are consistent between the two analyses.

@@

From the model 4 in @reich:2013:DJP, we know that the standardized beta coefficients for the variables rank and professional experience are .15 and .07 respectively. Unfortunately, the associated standard errors (or standard deviations) were not reported but only asterisks representing statistical significance (p < 0.001 for rank, p < 0.01 for professional experience). We estimated the maximum standard deviation based on the significance level. For example, the standard deviation of the standardized regression coefficient ($\sigma_{\beta'_{1}}$) of rank can be estimated by solving [^wald]:

@@

or in R

```r
beta_d_1 <- 0.15
sig_level <- 0.001
beta_d_1 / abs(qnorm(sig_level / 2))
```

@@

The following is the complete code to construct the two Bayesian models. The cubic relationship can be set using the `I()` function.

```r
require(tidyverse)

informative_prior <- c(prior_string("normal(0, 1)", class = "b"),
                       prior_string("normal(0, 1)", class = "Intercept"),
                       prior_string("normal(0.14, 0.045)",
                                    class = "b", coef = "EXPRNCE"),
                       prior_string("normal(0.07, 0.027)",
                                    class = "b", coef = "RANK"))

std <- function(x){
  (x - mean(x, na.rm = TRUE))/sd(x, na.rm = TRUE)
}
## eiu is Index of Democracy, gdppc is GDP per capita (log)
set.seed(12121)
wjs %>%
    select(ppa, EXPRNCE, RANK, GENDER, UNI_EDU, UNI_EDU, eiu, gdppc, COUNTRY) %>%
    mutate(gdppc = log(gdppc), COUNTRY = as.factor(COUNTRY)) %>%
    mutate_at(vars(ppa:gdppc), std) -> wjs_processed
brm(ppa ~ EXPRNCE + RANK + GENDER + UNI_EDU + eiu + gdppc + (1|COUNTRY),
    data = wjs_processed, cores = 4, iter = 3000, prior = informative_prior,
        sample_prior = TRUE) -> ppa_mod

set.seed(12121)
## iter needs to set larger to ensure convergence
brm(ppa ~ EXPRNCE + RANK + GENDER + UNI_EDU + I(eiu^3) + gdppc + (1|COUNTRY),
    data = wjs_processed, cores = 4, iter = 4000, prior = informative_prior,
    sample_prior = TRUE) -> ppa_qmod
```

@@

[^wald]: Here we used the z-approximation of Wald test rather than the more typical t-distribution-based Wald test because the degree of freedom (df) is not reported. And t-distribution approximates z-distribution asymptotically when df gets larger.

>>>>

authornote: |
  The authors would like to thank professor Kasper Welbers (Vrije Universiteit Amsterdam) for his advice on the development of the Dutch dictionary; Dr Junior Yuner Zhu (City University of Hong Kong) for sharing details about her study.  The authors report there are no competing interests to declare.
  Source code and data are available at (redacted). Prereg: https://osf.io/2h4w8/

@@

<!-- *"The comparative approach attempts to reach conclusions beyond single cases and explains differences and similarities between objects of analysis against the backdrop of their contextual conditions."* @esser:2017:CRM -->

@@

This study of ecological effects on individual behaviors has a long tradition in social sciences. A famous example was Émile Durkheim's investigation on the ecological factors associated with suicide [@durkheim1897suicide]. Durkheim found a higher suicide rate among citizens from Scandinavian countries than those from other European countries. Using today’s standard, Durkheim's analysis is descriptive and this descriptive approach for studying ecological effect is indeed still useful for hypothesis generation in comparative research. An example of hypothesis-generating comparative research is <!-- redacted for ijoc  -->AUTHOR1 <!-- @chan2020combining -->, in which the sentiment profiles of terrorism coverage from Muslim- and Christian-majority countries were visualized. Hypothesis-generating comparative study, however, is rare. Most studies have a confirmatory outlook. As we see from the example hypotheses above, most of these studies propose hypotheses to test for ecological effects. In this context usually traditional (frequentist) hypothesis testing approaches were used: @esser:2013:C lumped multiple outlets from the same country together and then used univariate analysis of variance to test for the differences in the proportion of opinion-orienting articles across countries. In @wu:2000:SDI, multiple stepwise regression was used. These approaches violate the underlying assumptions of the statistical analyses. It highlights the fact that comparative research introduces a feature that researchers usually overlook: media contents are clustered in a multilevel structure. A news article is nested within its media outlet and its media outlet is in turn nested within its country. Such data structure brings two problems: non-atomicity and non-stochasticity.

@@

This method is the so-called "disaggregation approach". From an epistemic standpoint, searching for ecological effect by studying the value of slope ($\beta_{1}$) leads to atomistic fallacy [@hox2017multilevel]. From a statistical standpoint, this approach violates the underlying independence assumption. Almost all frequentist statistical tests assume that the observations are independent of each other: $y_{i}$ given $x_{i}$ are independently identically distributed (i.i.d.). Articles from the same media outlet are hardly i.i.d.: they are subjected to being edited by the same editorial team, to being written by the same group of journalists exposed to the same journalistic culture and paid for by the same employer. Also, the way communication researchers collect their media content resembles cluster sampling rather than random sampling: one usually starts from a specific media outlet and then collects all relevant articles from it. The choice of media outlets or countries is almost always not randomly selected. <!-- [^1] --> This sampling approach makes the independence assumption even more fragile.

<!-- [^1]: If countries were randomly selected, we shall see more African countries in comparative works. It is because 1/4, or 54 out of 195, UN countries are in Africa. -->

Previous simulation studies have shown that ignoring this dependence can lead to false-positive associations [e.g. @clarke:2008:W;@chen:2012:IIL]. The problem is more severe when the dependent variable is a discrete binary variable [@clarke:2008:W], a common feature of content analysis. <!-- [^2] -->

<!-- [^2]: The non-atomicity argument has been in standard statistics textbooks for 40+ years and it might look repetitious. We believe it is still necessary, not least because multilevel modeling --unlike what @mcelreath2020statistical [p. 356] said-- is still not the default regression approach in communication research for hierarchical data and there are many justifications for using the disaggregation approach, e.g. an example in @zhu:2020:S [footnote 5]. <\!-- Even a multilevel modeling textbook advocates these justifications [@bickel2007multilevel]. -\-> See also @nezlek:2008:IMM for a criticism of these justifications.  -->

@@

What is the probability for this paper being accepted by *IJOC*? Under the frequentist framework (and if *IJOC* were accepting papers stochastically), we can only find this out by repeatedly submitting this paper to *IJOC*, say for 100 times, and then count the frequency of acceptance in these repeated submissions. It is indeed impractical as well as inhumane to the editorial team of *IJOC*. Instead, we assert before submission that this paper has a probability of 24% for being accepted. That is the published acceptance rate of a similar journal. After this paper is submitted and is not desk rejected, the probability might be around 24% to 30%. After a month of waiting and our confidence is shaken a little, the probability might decrease to 10% to 20%. After the paper is favorably reviewed by two reviewers and an R&R is invited, the probability might increase to 40% to 60%. If you see this paper on *IJOC*'s website, then the probability is beyond doubt 100% (or 0% if we submit this paper again).

@@

Undoubtedly, setting prior is consequential to the analysis [@van:2006:PB]. But the influence from priors is greatly weakened, when the data is getting bigger. Other than expert elicitation, another non-controversial way to specify priors --- at least in our opinion --- is to use  a weakly informative prior [@lemoine:2019:M]. In this way, one specifies only the possible range of the posterior<!-- [^4] -->. Some so-called "default weakly informative priors", e.g. $\mathcal{t}(1, 0, 0.25)$, have been suggested for typical regression models [@gelman:2008]. The documentation of Stan also provides information on how to choose an appropriate prior (https://github.com/stan-dev/stan/wiki/Prior-Choice-Recommendations).

<!-- [^4]: One could also use a completely *noninformative* prior such as $\mathcal{U}(-\infty, \infty)$. It is, however, no longer advised. -->

@@

<!-- *"There is a general challenge to a prescription of more widespread use of Bayesian methods for multilevel modeling, and that is that such methods require statistical expertise beyond that of most applied social science researchers, as well as specialist software (or software with which such researchers are unfamiliar)."* @bryan:2015:MMC [p. 19] -->

Bayesian analysis is still a minority statistical method in social sciences. It is reasonable to say that Bayesian analysis is extremely rare in our field. Although some communication researchers adopted the method (e.g. AUTHOR2, AUTHOR3) <!-- [e.g. @kovic:2017:B;@chan2020high] -->, these studies are not comparative. As far as we know, the only available comparative research in journalism studies that Bayesian multilevel regression was used for studying ecological effect are @leeuw:2020:AAT and @heidenreich:2022:DE. We believe comparative communication research fits the use case of Bayesian multilevel regression analysis. Although there is another methodological introduction to Bayesian analysis aiming at communication researchers [@konijn:2015:PSP], one purpose of this paper is to demonstrate how to actually do the analysis using the R package *brms* [@burkner2017advanced] (see the source code in the Online Appendix https://osf.io/2h4w8/?view_only=be14dc637b8e4fd1a26ac5c64682b6d9 ). As the interface of *brms* is almost the same as *lme4* [@bates:2015:FLM, another R package for fitting multilevel models using MLE], *lme4* users might find *brms* extremely familiar. <!-- The above-quoted challenge about the prescription of more widespread use of Bayesian methods for multilevel modeling is no longer an issue.  -->

@@

We used only the data from 2019 as the baseline. <!-- It is important to note that the Hong Kong protests, the 30th anniversary of the Tiananmen Square Protests and the 70th anniversary of the communist regime were in that year. Also, it was at the zenith of the US-China trade war.  -->

@@

@@

@@

@@

@@

All, except the prior for regression coefficients, are default priors suggested by *brms*.

@@

[^5]: HDI is one representation of the Bayesian credible interval. There should be no "correct" choice of the level of credibility but some established conventions. We choose, like many published works [e.g. @stegmueller:2013:HMC<!-- ; @kovic:2017:B; @chan2020high -->], the default value of 95\%. However, there is a general concern about this credibility level as being unstable for Bayesian analysis [@kruschke2014doing]. <!-- Some Bayesians, notably Andrew Gelman, report very liberal 50\% credible intervals. @mcelreath2020statistical selects 89\% to show the arbitrariness of the practice. @leeuw:2020:AAT select 90\%. -->

@@

There are <!-- several --> two diagnostic checks that we can do to make sure our model is valid.

<!-- * Increasing number of iterations -->

<!-- The first test is to increase the number of iterations from 2000 to a higher value, e.g. 4000, and see if the result is consistent with the initial analysis. This check makes sure our result is not transient due to short iteration time. -->

<!-- Increasing the number of iterations did change a bit of the estimates, but only at the second decimal place. It shows that the results are consistent between the two analyses. -->

@@

From the model 4 in @reich:2013:DJP, we know that the standardized beta coefficients for the variables rank and professional experience are .15 and .07 respectively. Unfortunately, the associated standard errors (or standard deviations) were not reported but only asterisks representing statistical significance (p < 0.001 for rank, p < 0.01 for professional experience). We estimated the maximum standard deviation based on the significance level. For example, the standard deviation of the standardized regression coefficient ($\sigma_{\beta'_{1}}$) of rank can be estimated by solving <!-- [^wald] -->:

@@

@@

@@

<!-- [^wald]: Here we used the z-approximation of Wald test rather than the more typical t-distribution-based Wald test because the degree of freedom (df) is not reported. And t-distribution approximates z-distribution asymptotically when df gets larger. -->
